\chapter{Grammar of Entity Relationships}
\label{chp:grammar}

\section{Overview}

In this chapter, we describe how the glyphs of \SBGNERLone can be combined
to make a valid \ER{} map. To do this, we must at the very least
define what glyphs can be connected to each other. This is called
syntax. Next, we must define rules over and above connection rules,
such as whether duplicate symbols are permitted. In addition, we must define what the notation ``means'' --- how does it represent a body of biological knowledge? This is semantics, and it is essential if a reader is to understand an SBGN diagram without external help, and a writer is to create one that reflects his understanding of a biological system.

In this section we start off by describing the concepts of the
\ER{} notation. Next a detailed description of the syntax is provided
followed by a description of the syntactic rules of the notation.

\section{Concepts}

The SBGN \ER{} language is more than a collection of symbols. It is a
visual language that uses specific abstractions to describe the
biological processes that make up a quantitative model, a signalling pathway or a metabolic network. This abstraction is the semantics of SBGN, and to describe it requires more than a definition
of the symbols and syntax of the language. We first need to define the
abstractions we are using.

SBGN \ERs{} describe biological interactions involving biological entities. An \glyph{interactor} (\sect{interactors}), such as a molecule, influences the behaviour of other \glyph{interactor} via a relationships. 

It may be convenient to think of a SBGN \ERs{} as listing independent rules that decribe influences between interactors. Diagram can then be analysed with ``what if?'' queries. 

\input{sources/syntax.tex}

\input{sources/semantics.tex}
