% !TEX root = ../sbgn_ER-level1.tex
% =============================================================================
% introduction
% =============================================================================

\chapter{Introduction}

The goal of the \textbf{S}ystems \textbf{B}iology \textbf{G}raphical \textbf{N}otation (SBGN) is to standardize the graphical/visual representation of essential biochemical and cellular processes. SBGN defines comprehensive sets of symbols with precise semantics, together with detailed syntactic rules defining their use.  It also describes the manner in which such graphical information should be interpreted. For a general description of SBGN goals, one can read:

\begin{quote}
 Nicolas Le Nov\`{e}re, Michael Hucka, Huaiyu Mi, Stuart Moodie, Falk Schreiber, Anatoly Sorokin, Emek Demir, Katja Wegner, Mirit I Aladjem, Sarala M Wimalaratne, Frank T Bergman, Ralph Gauges, Peter Ghazal, Hideya Kawaji, Lu Li, Yukiko Matsuoka, Alice Villéger, Sarah E Boyd, Laurence Calzone, Melanie Courtot, Ugur Dogrusoz, Tom C Freeman, Akira Funahashi, Samik Ghosh, Akiya Jouraku, Sohyoung Kim, Fedor Kolpakov, Augustin Luna, Sven Sahle, Esther Schmidt, Steven Watterson, Guanming Wu, Igor Goryanin, Douglas B Kell, Chris Sander, Herbert Sauro, Jacky L Snoep, Kurt Kohn, Hiroaki Kitano. The Systems Biology Graphical Notation. Nature Biotechnology 27, 735 - 741 (2009).  \url{http://dx.doi.org/10.1038/nbt.1558}
\end{quote}

This document defines the \emph{\ER{}} visual language of SBGN. \ERs are one of three views of a biological process offered by SBGN, the others being \PDs and \AFs. SBGN \ERl{} allows to see all the relationships in which a given entity participates, regardless of the temporal aspects. Entities are defined here in a broad sense as something that can \corr{exists}{exist}. Relationships can be seen as rules describing the influences of entities on other relationships. An overview of \ERs is given in \sect{overview}.

\input{sources/er-overview.tex}
\input{sources/versioning.tex}
\input{sources/community.tex}
\input{sources/typography.tex}
