\chapter{Acknowledgments}\label{sec:acknowledgments}

SBGN specifications are developed by many people, and with the support of many organisations.

\section{Main contributors}

In addition to the SBGN editors, the specification of SBGN ER benefited enormously from the contribution of many people. In particular, the specification of \SBGNERLone benefited much from deep discussions with Mirit Aladjem, Kurt Kohn, Emek Demir, Augustin Luna, Sohyoung Kim, Yukiko Matsuoka and Hiroaki Kitano. 

\section{Comprehensive list of contributors}

Here is a more comprehensive list of people who have been actively involved in SBGN development, either by their help designing the languages, their comments on the specification, help with development infrastructure or any other useful input.  We aim this list to be rather complete. We are very sorry if we forgot someone, and will be grateful if you notified us of any omission.

Mirit Aladjemm, Frank Bergmann, Michael Blinov, Sarah Boyd, Laurence Calzone, Melanie Courtot, Tobias Czauderna, Emek Demir, Ugur Dogrusoz, Tom Freeman, Akira Funahashi, Ralph Gauges, Peter Ghazal, Samik Ghosh, Igor Goryanin, Michael Hucka, Akiya Jouraku, Hideya Kawaji, Douglas Kell, Sohyoung Kim, Hiroaki Kitano, Kurt Kohn, Fedor Kolpakov , Nicolas Le Nov\`{e}re, Lu Li, Augustin Luna, Yukiko Matsuoka, Huaiyu Mi, Stuart Moodie, Sven Sahle, Chris Sander, Herbert Sauro, Esther Schmidt, Falk Schreiber, Jacky Snoep, Anatoly Sorokin, Jessica Stephens, Linda Taddeo, Steven Watterson, Martijn van Iersel, Alice Vill\'{e}ger, Katja Wegner, Sarala Wimalaratne, Guanming Wu.

The authors are also grateful to all the attendees of the SBGN meetings, as well as to the subscribers of the sbgn-discuss@caltech.edu mailing list.

\section{Financial support}

The development of SBGN was mainly supported by a grant from the Japanese New Energy and Industrial Technology Development Organization (NEDO, \url{http://www.nedo.go.jp/}). The Okinawa Institute of Science and Technology (OIST, \url{http://www.oist.jp/}), the AIST Computational Biology Research Center (AIST CBRC, \url{http://www.cbrc.jp/index.eng.html}), the British Biotechnology and Biological Sciences Research Council (BBSRC, \url{http://www.bbsrc.ac.uk/}) through a Japan Partnering Award, the European Media Laboratory (EML Research gGmbH, \url{http://www.eml.org/english/}), and the Beckman Institute at the California Institute of Technology (\url{http://bnmc.caltech.edu}) provided additional support for SBGN workshops. Some help was provided by the Japan Science and Technology Agency (JST, \url{http://www.jst.go.jp/}) and the Genome Network Project of the Japanese Ministry of Education, Sports, Culture, Science, and Technology (MEXT, \url{http://www.mext.go.jp/}) for the development of the gene regulation network aspect of SBGN, and from the Engineering and Physical Sciences Research Council (EPSRC, \url{http://www.epsrc.ac.uk}) during the redaction of the specification.

