% =============================================================================
% glyphs
% =============================================================================

\chapter{Entity Relationship glyphs}
\label{chp:glyph}

This chapter provides a catalog of the graphical symbols available for representing entities in \ERms.  There are different classes of glyphs corresponding to different classes of entity nodes, statements and influences.

In \chap{grammar} beginning on page~\pageref{chp:grammar}, we describe the rules for combining these glyphs into legal SBGN \ERs, and in \chap{layout} beginning on page~\pageref{chp:layout}, we describe requirements and guidelines for the way that diagrams are visually organized.

\section{Overview}
 
\input{sources/er-overview.tex}
 
\section{Controlled vocabularies used in \SBGNERLone}\label{sec:CVs}

\input{sources/CVs.tex}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%                   Interactor nodes
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\section{Entity nodes}\label{sec:ENs}

\glyph{Entity nodes} (ENs) represent element of truth, things that exist. 
%In ontology parlance, they would be ``continuants''. 
Entity nodes are the source of influences. \SBGNERLone{} provides three different types of \glyph{entity nodes}, the \glyph{interactors}, the \glyph{logical operators} and the \glyph{perturbing agent}. 

\subsection{Interactors}\label{sec:interactors}

Interactors are entity nodes that are able to participate in an interaction (\sect{interaction}). \SBGNERLone{} provides two interactors, the \glyph{entity} and the \glyph{outcome} of a statement.

\input{sources/entity.tex}
\input{sources/outcome.tex}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%                   Logical operators
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Logical operators}\label{sec:logic}

A \glyph{logical operator} allows to combine elements of truth into another element of truth (if A exists and B exits, then A AND B exists) in order ot apply influences. \SBGNERLone{} provides four \glyph{logical operators}, \glyph{and}, \glyph{or}, \glyph{not} and \glyph{delay}.

\input{sources/and.tex}
\input{sources/or.tex}
\input{sources/not.tex}
\input{sources/delay.tex}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%                   Perturbing agent
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Glyph: \glyph{Perturbing agent}}\label{sec:perturbation}
\input{sources/perturbation.tex}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%                   Auxiliary units
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Auxiliary units}\label{sec:aux}

\glyph{Auxiliary units} are decorations used on \glyph{entities} (\sect{entity}) and \glyph{interactions} (\sect{interaction}) to further refine their semantics.  \SBGNERLone{} provides two \glyph{auxiliary units}, the \glyph{unit of information} and the \glyph{state variable}.

\input{sources/unitInformation.tex}
\input{sources/stateVariable.tex}
% \input{sources/domain.tex}               %%%%%% POSTPONED %%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Relationship arcs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Relationships}\label{sec:relationships}

\glyph{Relationships} are rules that decide of the existence of entity nodes, based on the existence of others. 
%In ontology parlance, they would be ``occurants''. 
\SBGNERLone{} provides two types of relationships, the statements and the influences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Statements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Statements}\label{sec:statements}

\glyph{Statements} can be true or false. \glyph{Statements} are targets of \glyph{influences}. They are not true themselves, but can carry truth element (\glyph{outcomes}, see \sect{outcome}). \SBGNERLone{} provides three types of statements, \glyph{assignment}, \glyph{interaction} and \glyph{phenotype}.

\input{sources/assignment.tex}
\input{sources/interaction.tex}
%\input{sources/non-interaction.tex}
\input{sources/phenotype.tex}

\subsection{Influences}\label{sec:influences}

Influence arcs represent the effect of an entity on another relationship. The symbols attached to their extremities precise their semantics. SBGN \ERs{}' influences can be viewed as logical rules linking \glyph{ENs} and other rules. \SBGNERLone{} provides seven influences, \glyph{modulation}, \glyph{stimulation}, \glyph{inhibition}, \glyph{necessaryStimulation}, \glyph{absoluteInhibition}, \glyph{absoluteStimulation}, \glyph{logicArc}.

\input{sources/modulation.tex}
\input{sources/stimulation.tex}
\input{sources/inhibition.tex}
\input{sources/necessaryStimulation.tex}
\input{sources/absoluteInhibition.tex}
\input{sources/absoluteStimulation.tex}
\input{sources/logicArc.tex}

%\section{Submap}\label{sec:submap}
%\input{sources/submap.tex}

\input{sources/annotation.tex}