\chapter{Grammar of Entity Relationships}
\label{chp:grammar}

\section{Overview}

In this chapter, we describe how the glyphs of \SBGNERLone can be combined
to make a valid \ERm{}. To do this, we must at the very least
define what glyphs can be connected to each other. This is called
syntax. Next, we must define additional rules, such as whether duplicate symbols are permitted. In addition, we must define what the notation ``means'' --- how does it represent a body of biological knowledge? This is semantics, and it is essential if a reader is to understand an SBGN map without external help, and a writer is to create a map that reflects his understanding of a biological system.

In this section we start off by describing the concepts of the
\ERl{}. A detailed description of the syntax is provided next,
followed by a description of the syntactic rules of the language.

\section{Concepts}

The SBGN \ERl{} is more than a collection of symbols. It is a
visual language that uses specific abstractions to describe the
biological processes that make up e.g. a quantitative model, a signalling pathway or a metabolic network. This abstraction is the semantics of SBGN, and to describe it requires more than a definition
of the symbols and syntax of the language. We first need to define the
abstractions we are using.

SBGN \ERs{} describe biological interactions involving biological entities. An \glyph{entity node} (\sect{ENs}), such as a molecule, influences the behaviour of other \glyph{entity nodes} via a relationships. 

It may be convenient to think of a SBGN \ERs{} as listing independent rules that describe influences between \glyph{entity nodes}. Map can then be analysed with ``what if?'' queries. 

\input{sources/syntax.tex}
\input{sources/semantics.tex}


